Very Preliminary Draft

### 2021-07-05 article/draft.tex
updates

One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through ranking. Facebook ranks each post and ad with a relevancy score, a high score leading to a high likelihood of the post or the ad appearing in someone’s newsfeed. Facebook can thus make a post or a whole account less visible by decreasing the rank of its content.\footnote{Lyons, T. (2018, May 22). The three-part recipe for cleaning up your news feed. Facebook Newsroom. \href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} Such {\it reduce} action should be visible in the engagement metrics of the posts: if a post reaches less users because of a lower ranking, it is less likely to receive likes, comments and shares.

Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.}, was classified among websites that have posted deceptive content according to FactCheck.org\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}, and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.} On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}.}

>>>>

One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through a ranking system. Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed. doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T. (2018, May 22). The three-part recipe for cleaning up your news feed. Facebook Newsroom. \href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} Such {\it reduce} measure should be visible in the engagement metrics of a given post. That is, if a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.

To illustrate, we investigate the case of the website $Infowars$. Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.}, was classified among websites that have posted deceptive content according to FactCheck.org\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}, and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.} On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}.}
